An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/sec_constraint_approach.tex
Added third property

@@

  - Using property 2

  - Negated property 2 \neg P:

    p1 + p2 + p3 >= 2
\end{verbatim}

@@

  - Using property 1

  - Negated property 1 \neg P:

>>>>

  - Property 3: Variable bit1 is either true or false

  - Property 3: bit1 + nbit1 = 1, alternatively written as
                bit1 + nbit1 <= 1 /\ bit1 + nbit1 >= 1

@@

  - Using property 1, with negated property \neg P:

    The constraints are satisfiable, therefore we can not
    prove safety with this method.

  - Using property 2, with negated property \neg P:

    p1 + p2 + p3 >= 2

    The constraints are unsatisfiable, therefore we
    prove safety with this method.

  - Using property 3, with negated property \neg P:

    nbit1 + nbit1 <= 0 \/ nbit1 + nbit1 >= 2

    The constraints are unsatisfiable, therefore we
    prove safety with this method.
\end{verbatim}

@@

  - Using property 1, with negated property 1 \neg P:
